Age-related changes in plant growth and traits

### 2015-09-08 RA_combined_plots.Rmd
additions to plots

>>>>

#modified; original below
```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
par(mfcol=c(4,3), cex=1, omi=c(.1,.3,.3,.1), mai=c(1.1,1,.1,0.1)) 
yvar <- "leaf_area"
yvar2 <- "height"
yvar3 <- "total_inv"
yvar4 <- "RA_leaf_area"
xvar <- "leaf_area_midyear"
xvar2 <- "age"
xvar3 <- "height"

data2 <- subset(SummarySppAge[["mean"]])
data2 <- split(data2, data2$species)

  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",xlab="leaf area (midyear)",ylab="total investment (mg)",cex=1.3,
                    col=col.age(data[[spp]]$age),main=spp)
  arrows(data[[spp]]$leaf_area_midyear,data[[spp]]$growth_inv,data[[spp]]$leaf_area_midyear,data[[spp]]$total_inv,length = 0, angle = 30, code = 2, col = "black",lwd=1)
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar2,log="x",xlab="age",ylab="RA",cex=1.3,ylim=c(0,1.4),
                    col=col.age(data[[spp]]$age))
  points(RA_leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="age",ylab="final leaf area",cex=1.3,
                    col=col.age(data[[spp]]$age))
  points(leaf_area~age,data2[[spp]],pch=16)
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar2,log="xy",xlab="age",ylab="height",cex=1.3,
                    col=col.age(data[[spp]]$age))
  points(height~age,data2[[spp]],pch=16)
  }
```

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=18, fig.height=15}
par(mfcol=c(2,2), cex=1, omi=c(.1,.3,.3,.1), mai=c(1.1,1,.1,0.1)) 
xvar <- "age"

yvar1 <- "height"
yvar2 <- "diameter"
yvar3 <- "leaf_area"
yvar4 <- "total_weight_0"

  plot_yvar_vs_xvar(data[[spp]], yvar1, xvar,log="xy",ylab="height",xlab="age",cex=1.3,
                    col=col.age(data[[spp]]$age),main=spp)
  plot_yvar_vs_xvar(data[[spp]], yvar2, xvar,log="xy",ylab="diameter",xlab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar3, xvar,log="xy",ylab="leaf area",xlab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar4, xvar,log="xy",ylab="weight",xlab="",cex=1.3,
                    col=col.age(data[[spp]]$age))
  }
```

### 2015-09-08 RA_figs.rmd
additions to plots

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")

@@

@@

>>>>

SummaryInd <- readRDS("export/SummaryInd.rds")
SummarySpp <- readRDS("export/SummarySpp.rds")
SummarySppAge <- readRDS("export/SummarySppAge.rds")
HarvestData <- readRDS("export/HarvestData.rds")
InvestmentByPart <- readRDS("export/Investment_FD_all.rds")

@@

data <- subset(SummaryInd, age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

@@

data <- subset(SummaryInd,age>2)
data <- split(data, data$species)
lmfits <- lapply(data, function(x) lm(log10(x[[yvar]]) ~  (log10(x[[xvar]]))))
results <- summarise_all_fits(lmfits)

### 2015-09-08 tests.Rmd
additions to plots

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "shoot_leaf_area"
xvar <- "leaf_area"

@@

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(1.1,.7,.6,0.2)) 
yvar <- "growth_height_log"
xvar <- "RA"
xvar2 <- "growth_inv"

data <- subset(SummaryInd,reproducing==TRUE&age>2)
data <- split(data, data$species)

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar,log="",xlab="repro",ylab="",cex=1.3, main=spp,col=col.age(data[[spp]]$age))
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="x",xlab="veg", ylab="", cex=1.3, main=spp,col=col.age(data[[spp]]$age))
}

@@

>>>>

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.7,.9,.4,0.2)) 
yvar <- "shoot_leaf_area"
xvar <- "initial_leaf_area"

@@

SummaryInd$growth_height_per <- SummaryInd$growth_height/SummaryInd$height_0
SummaryInd$growth_leaf_per <- SummaryInd$growth_leaf/SummaryInd$leaf_weight
SummaryInd$growth_leaf_pos <- SummaryInd$growth_leaf

```{r, echo=FALSE,message=FALSE,warning=FALSE, fig.width=20, fig.height=20}
par(mfrow=c(4,4), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.7,.6,0.2)) 
yvar <- "growth_leaf_per"
xvar2 <- "diameter"

for(spp in names(data)) {
  plot_yvar_vs_xvar(data[[spp]], yvar, xvar2,log="xy",xlab="", ylab="", cex=1.3, main=spp,col=col.age(data[[spp]]$age))
}

mtext("Height growth (%)", 2, outer=TRUE,cex=1.2)
mtext("diameter", 1, outer=TRUE,cex=1.2)
legend("topleft",legend=labels.age(),col=col.age(),pch=16, cex=1.1,bty="n")
```

@@

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.3,.6,0.2)) 
data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
plot(leaf_weight~diameter,data[[spp]],log="xy",cex=1.3, main=spp,col=col.age(data[[spp]]$age),pch=16)
points(leaf_weight_0~diameter_0,data[[spp]],cex=1.3,pch=1,col=col.age(data[[spp]]$age))
arrows(data[[spp]]$diameter, data[[spp]]$leaf_weight, data[[spp]]$diameter_0,data[[spp]]$leaf_weight_0, length = 0,angle = 30, code = 2, col = col.age(data[[spp]]$age),lwd=.3)
}
```

```{r}
par(mfrow=c(2,2), cex=1, omi=c(.7,.7,.1,.1), mai=c(.3,.3,.6,0.2)) 
data <- subset(SummaryInd)
data <- split(data, data$species)

for(spp in names(data)) {
plot(stem_weight~diameter,data[[spp]],log="xy",cex=1.3, main=spp,col=col.age(data[[spp]]$age),pch=16)
points(stem_weight_0~diameter_0,data[[spp]],cex=1.3,pch=1,col=col.age(data[[spp]]$age))
arrows(data[[spp]]$diameter, data[[spp]]$stem_weight, data[[spp]]$diameter_0,data[[spp]]$stem_weight_0, length = 0,angle = 30, code = 2, col = col.age(data[[spp]]$age),lwd=.3)
points(leaf_weight~diameter,data[[spp]],cex=1.3,pch=17,col=col.age(data[[spp]]$age))
points(leaf_weight_0~diameter_0,data[[spp]],cex=1.3,pch=2,col=col.age(data[[spp]]$age))
arrows(data[[spp]]$diameter, data[[spp]]$leaf_weight, data[[spp]]$diameter_0,data[[spp]]$leaf_weight_0, length = 0,angle = 30, code = 1, col = col.age(data[[spp]]$age),lwd=.3,lty=3)
}
```
